Parsing Postfix log files

### 2009-03-03 doc/logparser-architecture.tex
Wrote priority/rule ordering paragraph; it turned out that a whole section was overkill.

    \item [Classify the input]  The pseudo-code above shows how rules are
        successively tried until one is found that recognises the current
        input.  That pseudo-code is very simple: there may be efficiency
        concerns, (\sectionref{parser efficiency}), rule conditions
        (\sectionref{attaching conditions to rules}), or prioritisations
        (\sectionref{prioritisation and rule ordering}) that complicate the
        process.

@@

Rules are responsible for categorising inputs: each rule should recognise
one and only input variant.  An input category with multiple input variants
should have multiple rules, one for each variant.  Rules will typically use
a regex when classifying inputs, but other approaches may prove useful for
some applications, e.g.\ comparing fixed strings to the input, or checking
the length of the input; for the remainder of this thesis it will be
assumed that a regex is used.  Each rule must specify at least the regex to
recognise inputs and the action to invoke when classification is
successful, but implementations are free to add any other attributes they
require; \sectionref{rule attributes} describes the attributes used in
\parsername{}, and some potential attributes will be discussed later in
this section (\sectionref{attaching conditions to rules} and
\sectionref{prioritisation and rule ordering}).  Classifying inputs using
the rules is simple: the first rule to recognise the input determines the
action that will be invoked: there is no backtracking to try alternate
rules; no attempt is made to pick a \textit{best\/} rule.

@@

An example of how rule conditions can be useful is parsing C-style
comments, which start with \texttt{/*} and end with \texttt{*/}; the start
and end tokens can be on one line, or may have many lines between them.
\Tableref{Rules to parse C-style comments} shows the regexes, conditions,
and state changes of the four rules required to parse C-style comments.
These rules are somewhat simplified, e.g.\ rules one and two will recognise
the comment start token even if it is within a quoted string, which is
incorrect.  Rules one and two will only be used when the parser is parsing
code, not comments: rule one recognises a comment that is contained within
one line and leaves the parser's state unchanged; rule two recognises the
start of a command and changes the parser's state to parsing comments.
Rules three and four will be used when the parser is parsing a comment:
rule three recognises the end of a comment and switches parsing state back
to parsing code; rule four recognises a comment line without an end token
and keeps the parser's unchanged.  It is important that the rules are
applied in the order listed in \tableref{Rules to parse C-style comments};
\sectionref{prioritisation and rule ordering} explains how this is
achieved.

@@

\subsection{Prioritisation and Rule Ordering}

\label{prioritisation and rule ordering}

XXX PRIORITY ATTRIBUTE AND RULE ORDERING\@.

The first matching rule wins: no further rules are tried against that
input, but there is a mechanism for prioritising the rules so that more
specific rules can be tried first.

>>>>

    \item [Classify the input]  The pseudo-code above shows how rules are
        successively tried until one is found that recognises the current
        input.  That pseudo-code is very simple: there may be efficiency
        concerns, (\sectionref{parser efficiency}), rule conditions
        (\sectionref{attaching conditions to rules}), or prioritisations
        (\sectionref{rules in architecture}) that complicate the process.

@@

Rules are responsible for categorising inputs: each rule should recognise
one and only input variant.  An input category with multiple input variants
should have multiple rules, one for each variant.  Rules will typically use
a regex when classifying inputs, but other approaches may prove useful for
some applications, e.g.\ comparing fixed strings to the input, or checking
the length of the input; for the remainder of this thesis it will be
assumed that a regex is used.  Each rule must specify at least the regex to
recognise inputs and the action to invoke when classification is
successful, but implementations are free to add any other attributes they
require; \sectionref{rule attributes} describes the attributes used in
\parsername{}, and some potential attributes will be discussed later in
\sectionref{attaching conditions to rules}.

Classifying inputs using the rules is simple: the first rule to recognise
the input determines the action that will be invoked: there is no
backtracking to try alternate rules; no attempt is made to pick a
\textit{best\/} rule.  \sectionref{attaching conditions to rules} contains
an example which requires that the rules are used in a specific order to
correctly parse the input, so a mechanism is needed to allow the author of
the rules to specify that ordering.  The framework should be written so
that it sorts the rules according to a priority attribute specified by the
rule author, allowing fine-grained control over the order that rules are
used in.  The priority attribute may be implemented as a number, or as a
range of values, e.g.\ low, medium, and high, or in a different fashion
entirely if it suits the implementation.  Rule ordering for efficiency is a
separate topic that is covered in \sectionref{rule ordering for
efficiency}; overlapping rules are discussed in \sectionref{overlapping
rules in architecture}.

@@

An example of how rule conditions can be useful is parsing C-style
comments, which start with \texttt{/*} and end with \texttt{*/}; the start
and end tokens can be on one line, or may have many lines between them.
\Tableref{Rules to parse C-style comments} shows the regexes, conditions,
and state changes of the four rules required to parse C-style comments.
These rules are somewhat simplified, e.g.\ rules one and two will recognise
the comment start token even if it is within a quoted string, which is
incorrect.  Rules one and two will only be used when the parser is parsing
code, not comments: rule one recognises a comment that is contained within
one line and leaves the parser's state unchanged; rule two recognises the
start of a command and changes the parser's state to parsing comments.
Rules three and four will be used when the parser is parsing a comment:
rule three recognises the end of a comment and switches parsing state back
to parsing code; rule four recognises a comment line without an end token
and keeps the parser's unchanged.  It is important that the rules are
applied in the order listed in \tableref{Rules to parse C-style comments};
\sectionref{rules in architecture} has explained how this is achieved, and
\sectionref{overlapping rules in architecture} discusses overlapping rules.

@@
